Parallel Adaptive Importance Sampling

### 2016-12-05 PAIS.tex
references fixed
added 'cost per sig fig' comparison to AMR section

In practice, the PMC algorithm can suffer from spiky posteriors due to
poor approximation properties in some parts of the posterior. The
adaptive multiple importance sampling algorithm
(AMIS)~\cite{cornuet2012adaptive} aims to reduce the impact of these
poor approximations. AMIS considers the entire sample at time $n$ to
be a draw from all approximations up to time $n$. This means that the
importance weights for the whole sample must be recalculated at each
iteration. These weights are known as deterministic mixture
weights~\cite{owen2000safe,veach1995optimally}, where the denominator
is the sum of all kernels, $q_t(\cdot), 0\leq t\leq n$,
\[
	w_n = \pi(Y_n) \Big/ \sum\limits_{t=0}^n \! q_t(Y_n).
\]
The advantage of this system is that at a time $n_1$ a region might be
badly approximated, it might be better approximated at a later time
$n_2$, so the weight for the sample $Y_{n_1}$ will be more
representative of the density in that region, if it is considered as a
draw from a mixture of samples up to time $n_2$. These weights are
however biased, consistency was proved in~\cite{marin2014consistency}.
AMIS has been successfully implemented for problems in population
genetics~\cite{siren2011reconstructing}.

@@

\begin{figure}[htb]
\centering
\subfigure[Relative error in $\mathbb{E}(X)$]{\includegraphics[width=0.45\textwidth]{"figures/Resampler_EX"}}
\subfigure[Relative error in
$\mathbb{E}(X^2)$]{\includegraphics[width=0.45\textwidth]{"figures/Resampler_EX2"}}\\
\subfigure[Relative error in $\mathbb{E}(X^3)$]{\includegraphics[width=0.45\textwidth]{"figures/Resampler_EX3"}}
\subfigure[Cost of resamplers per iteration]{\includegraphics[width=0.45\textwidth]{"figures/Resampler_speed"}}\\
\caption{Finding optimal values of $\beta$ for the problem in Section~\ref{sec:problem 1}. The setup is as in Section~\ref{sec:Implementation P1}.}
\label{fig:AMR}
\end{figure}

>>>>

In practice, the PMC algorithm can suffer from spiky posteriors due to
poor approximation properties in some parts of the posterior. The
adaptive multiple importance sampling algorithm
(AMIS)~\cite{cornuet2012adaptive} aims to reduce the impact of these
poor approximations. AMIS considers the entire sample at time $n$ to
be a draw from all approximations up to time $n$. This means that the
importance weights for the whole sample must be recalculated at each
iteration. These weights are known as deterministic mixture
weights~\cite{owen2000safe,veach1995optimally}, where the denominator
is the sum of all kernels, $q_t(\cdot), 0\leq t\leq n$,
\[
	w_n = \pi(Y_n) \Big/ \sum\limits_{t=0}^n \! q_t(Y_n).
\]
The advantage of this system is that at a time $n_1$ a region might be
badly approximated, it might be better approximated at a later time
$n_2$, so the weight for the sample $Y_{n_1}$ will be more
representative of the density in that region, if it is considered as a
draw from a mixture of samples up to time $n_2$. These weights are
however biased, consistency was proved in~\cite{marin2012consistency}.
AMIS has been successfully implemented for problems in population
genetics~\cite{siren2011reconstructing}.

@@

\begin{figure}[htb]
\centering
\subfigure[Relative error in $\mathbb{E}(X)$]{\includegraphics[width=0.45\textwidth]{"figures/Resampler_EX"}}
\subfigure[Relative error in
$\mathbb{E}(X^2)$]{\includegraphics[width=0.45\textwidth]{"figures/Resampler_EX2"}}\\
\subfigure[Relative error in $\mathbb{E}(X^3)$]{\includegraphics[width=0.45\textwidth]{"figures/Resampler_EX3"}}
\subfigure[Cost of resamplers per significant figure]{\includegraphics[width=0.45\textwidth]{"figures/Resampler_speed"}}\\
\caption{Comparison of the performance between different resampling schemes. The example in Section~\ref{sec:problem 1} is implemented for this demonstration.}
\label{fig:AMR}
\end{figure}
